The SMT Competition 2015--2018

### 2019-03-22 2018/report/SMT-COMP.tex
Report: Description of app track plot.

\begin{figure}
  \centering
  \scalebox{.45}{\includegraphics{%
  plot/pdf/bar_plot-Virtual_Best_Solver_(VBS)_Application_Track_2015-2018.pdf}}
  \vspace{-5ex}
  \caption{VBS in terms of correct \texttt{check-sat} answers
  (out of 30370517 total)
  within a time limit of 1200s
  on common benchmarks 2015-2018 of all logics in the Application
  track.}
  \label{fig:progress-all-app}
\end{figure}

@@

The SMT Competition consists of several tracks with a multitude of divisions
per track.
Not all participating solvers enter all tracks, and the majority of
participants participates only in a handful of divisions.
To give a measure of overall progress in solver performance we
use the notion of \emph{virtual best solver} (VBS) over all divisions of the
Main track.
We determine the VBS as the best wall-clock performance per (correctly solved)
instance with the time limit of 1200s used in the competitions 2017 and 2018.
Figure~\ref{fig:progress} visualizes VBS performance on common benchmarks over
pairs of consecutive years from 2014 to 2018 as a cactus plot.
It shows the wall-clock solving time per instance over all instances, sorted by
solving time.

Between 2014 (67426 benchmarks) and 2015 (154238 benchmarks),
the number of common benchmarks is 67070;
between 2015 and 2016 (154424 benchmarks) it is 154238;
between 2016 and 2017 (238758 benchmarks) it is 145236;
and between 2017 and 2018 (333241 benchmarks) it is 226429.
The number of solved instances on these sets of common benchmarks
increased from 2014 to 2015 by 0.1\%, from 2016 to 2017 by 3.9\%,
and from 2017 to 2018 by 0.3\%.
Interestingly, it decreased from 2015 to 2016 by 3.5\%.
This is mainly due to the fact that in 2015, more than 5600 benchmarks of
division QF\_FP where solved by one of the two participating configurations of
Z3 that no one else could solve, and in 2016 Z3 did not participate in this
division.

>>>>

\begin{figure}
  \centering
  \scalebox{.45}{\includegraphics{%
  plot/pdf/bar_plot-Virtual_Best_Solver_(VBS)_Application_Track_2015-2018.pdf}}
  \vspace{-5ex}
  \caption{VBS in terms of correct \texttt{check-sat} answers
  (out of 30370517 total)
  within a time limit of 2400s
  on common benchmarks 2015-2018 of all logics in the Application
  track.}
  \label{fig:progress-all-app}
\end{figure}

@@

The SMT Competition consists of several tracks with a multitude of divisions
per track.
Not all participating solvers enter all tracks, and the majority of
participants participates only in a handful of divisions.
To give a measure of overall progress in solver performance we
use the notion of \emph{virtual best solver} (VBS) over all divisions of all
three tracks.

For the Main track, we determine the VBS as the best wall-clock performance per
(correctly solved) instance with the time limit of 1200s used in the
competitions 2017 and 2018. Figure~\ref{fig:progress-all} visualizes VBS
performance on common benchmarks from 2015-2018 as cactus plot.
Figure~\ref{fig:progress} shows VBS performance on common benchmarks over pairs
of consecutive years from 2014 to 2018.  Both plots show the wall-clock solving
time per instance over all instances, sorted by solving time.
%
Between 2014 (67426 benchmarks) and 2015 (154238 benchmarks),
the number of common benchmarks is 67070;
between 2015 and 2016 (154424 benchmarks) it is 154238;
between 2016 and 2017 (238758 benchmarks) it is 145236;
and between 2017 and 2018 (333241 benchmarks) it is 226429.
The number of solved instances on these sets of common benchmarks
increased from 2014 to 2015 by 0.1\%, from 2016 to 2017 by 3.9\%,
and from 2017 to 2018 by 0.3\%.
Interestingly, it decreased from 2015 to 2016 by 3.5\%.
This is mainly due to the fact that in 2015, more than 5600 benchmarks of
division QF\_FP where solved by one of the two participating configurations of
Z3 that no one else could solve, and in 2016 Z3 did not participate in this
division.

For the Application track, we determine the VBS as the best performance in
terms of number of correct \texttt{check-sat} answers within the time limit
of 2400s (the time limit of the Application track in the competitions
2015-2018).
The total number of eligible \texttt{check-sat} queries (i.e., all queries with
status sat or unsat up to the first query with status unknown) on
common benchmarks from 2015-2018 is 30370517.
Figure~\ref{fig:progress-all-app} visualizes VBS performance on these
benchmarks as a bar plot.
In 2015, already 99.95\% of the eligible queries were answered correctly,
which naturally does not leave a lot of room for improvement.
In 2016, performance decreased by 185625 correct answers (0.61\%),
which can be entirely attributed to a performance degression
of Z3 on 2 benchmarks in the QF\_NIA division.
%(on which in 2016, CVC4 then
%performed best, and from 2017 onwards even as well as Z3 in 2015).
